%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% From Ken: For a faculty position, use the following order:
%
%Education
%Honours & Awards
%Publications
%Submitted Manuscripts
%Presentations
%
%then
%Professional Experience
%Teaching Experience
%Volunteer and Related Experience
%etc.

%------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{etaremune}% reverse enumerate

\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

% bibtex
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,maxcitenames=2,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

\addbibresource{/Users/thea/references.bib}

\AtEveryBibitem{%
    \clearfield{note}
    \clearfield{month}
    \clearfield{url}
}

% \pbox for two-column contact info
\usepackage{pbox}

% Hyper links and PDF info
\usepackage{hyperref}
\hypersetup{%
  colorlinks  = true,
  allcolors   = black
}


\usepackage{fontawesome}
\usepackage{academicons}

%----------------------------------------------------------------------------------------

\name{Thea Knowles} % Your name
\address{PhD, CCC-SLP}
%%\address{Buffalo, NY} % Your address
%%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%%\address{theaknow@buffalo.edu} % Your phone number and email
%\address{\emph{Last updated: \today}}
%
\begin{document}
\center{\em{Last updated:} \today}

\begin{flushleft}
  \pbox[t]{\textwidth}{%
    Oyer Speech \& Hearing Building, room 205\\
    1026 Red Cedar Rd.\\
    Department of Communicative Sciences \& Disorders\\
    Michigan State University\\
    East Lansing, MI 48824
  }
  \hfill
  \pbox[t]{\textwidth}{%
    \makebox[15pt][c]{\faEnvelope} \href{mailto:thea@msu.edu}{\ttfamily thea@msu.edu}\\
%    \makebox[15pt][c]{\faBriefcase} \href{https://arts-sciences.buffalo.edu/cds/people/academicfaculty/TheaKnowles.html}{\ttfamily Faculty Webpage}\\
     \makebox[15pt][c]{\faGlobe} \href{http://casa-lab.com/}{\ttfamily CASA Lab: casa-lab.com}\\
  }
\end{flushleft}


%-----
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{theaknow@buffalo.edu} % Your phone number and email


%\begin{document}
%\center{Lab website: \\ \url{https://www.casa-lab.com}}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment}

{{\bf Assistant Professor} (tenure system)} \hfill {Fall 2022 - present} \\
\emph{\bf{Director of Clinical Applications of Speech Acoustics Laboratory}}\\
Communicative Sciences \& Disorders \\
Michigan State University \\
East Lansing, MI

\bigskip \\

{{\bf Assistant Professor} (tenure system)} \hfill {2019 - Summer 2022} \\
\emph{\bf{Director of Clinical Applications of Speech Acoustics Laboratory}}\\
Communicative Disorders \& Sciences \\
University at Buffalo \\
Buffalo, NY


\end{rSection}

\begin{rSection}{Education}

{\bf Western University, London, ON} \hfill {2014 - 2019} \\ 
PhD, Speech \& Language Sciences  \\
Health \& Rehabilitation Sciences \bigskip \\

{\bf Western University, London, ON} \hfill {2014 - 2019} \\ 
MClSc, Speech-Language Pathology  \\
Communication Sciences \& Disorders (combined MClSc/PhD) \bigskip \\

%Speech-Language Science/Speech-Language Pathology 
{\bf McGill University, Montr\'eal, QC} \hfill {2008 - 2012} \\
B.A. Honours, Linguistics \\
First Class Honours, Distinction

\end{rSection}

%------------------------------
%	FUNDING
%------------------------------
\begin{rSection}{Grant and funding activity}

\begin{center}
	{\bf \emph{Research}}
\end{center}

\begin{rSubsection}{ASH Foundation New Investigators Research Grant}{2021}{American Speech-Language-Hearing Foundation}{}
	\item Value: \$10,000; Role: PI
\end{rSubsection}

\begin{rSubsection}{ASHA Advancing Academic-Research Careers Award}{2021}{American Speech-Language-Hearing Association}{}
	\item Value: \$5,000
\end{rSubsection}

\begin{rSubsection}{Ontario Graduate Scholarship}{2017, 2018}{Province of Ontario Graduate Scholarship Program}{}
	\item Value: \$15,000 CAD annually
	\item Competitive (merit-based) scholarship
\end{rSubsection}

\begin{rSubsection}{Graduate Student Research Program Award}{2017}{Parkinson Society Southwestern Ontario}{}
	\item Value: \$20,000 CAD
	\item Competitive
\end{rSubsection}
%
%\begin{rSubsection}{University at Buffalo start-up package}{2019-2022}{}{}
%	\item Value: \$275,500
%\end{rSubsection}


%\newpage
%%%%
\begin{center}
	{\bf \emph{Clinical}}
\end{center}

\begin{rSubsection}{Parkinson Voice Project SPEAK OUT!\textregistered \ and LOUD Crowd\textregistered \ Grant}{2020, 2021}{}{} %Current value: \$19,000 annually}{}
	\item Value: Supports continuation of the SPEAK OUT!\textregistered \ and LOUD Crowd\textregistered \ programs at the University at Buffalo Speech, Language, and Hearing Clinic, including Parkinson Voice Project consultation, access to graduate student training, clinic resources, and opportunity to receive monetary funding to support LOUD Crowd\textregistered \ groups in 2020 \& 2021
	\item Role: Lead Speech-language pathologist
\end{rSubsection}



%%%%
%\begin{center}
%	{\bf \emph{Internal Funding}}
%\end{center}
%
%\begin{rSubsection}{Western Graduate Research Scholarship}{2014 - 2019}{Western University Graduate Student Funding}{} %Current value: \$19,000 annually}{}
%	\item Value: approx. \$19,000 CAD annually
%	\item Western University graduate student stipend
%\end{rSubsection}

%%%%
%\begin{center}
%	{\bf \emph{Submitted or in preparation}}
%\end{center}
%
%\begin{rSubsection}{ASH Foundation New Investigators Grant}{2021-2022}{American Speech-Language-Hearing Foundation}{}
%	\item Proposal: "Effects of prominence and communicative intent in dysarthria"
%\end{rSubsection}
%
%\begin{rSubsection}{ASHA Advancing Academic Research Careers Award}{2021-2023}{American Speech-Language-Hearing Association}{}
%	\item Proposal: "Amplifying the voices of Parkinson’s disease: A mixed-methods exploration of the use of augmentative speech amplification technology for hypophonia in Parkinson’s disease"
%\end{rSubsection}




%\begin{center}
%	{\bf \emph{Unfunded}}
%\end{center}
%
% UB Humanities Institute
%
%\begin{rSubsection}{ASH Foundation Speech Science Research Grant}{2022-2023}{American Speech-Language-Hearing Foundation}{}
%	\item Proposal: "Effects of face masks and speech amplification devices in hypophonia"
%\end{rSubsection}
%
%\begin{rSubsection}{ASHFoundation New Investigators Research Grant}{2020}{American Speech-Language-Hearing Foundation}{}
%	\item Proposed Project Title: Effects of Prominence on Acoustic Distinctiveness and Intelligibility in Dysarthria
%	\item "The New Investigators Research Grant is designed to help further new investigators' research activities by funding preliminary studies that could launch larger-scale research studies."
%\end{rSubsection}
%
%\begin{rSubsection}{ASHA Advancing Academic-Research Careers}{2020}{American Speech-Language-Hearing Association}{}
%	\item ``The Advancing Academic-Research Careers (AARC) Award is intended to support the academic-research careers of junior-level faculty in the discipline of communication sciences and disorders (CSD). AARC is an award that supports mentored activities in both teaching and research."
%\end{rSubsection}
%
%%\begin{rSubsection}{Graduate Studentship Award}{2017}{Parkinson Society Canada}{}
%%\end{rSubsection}
%
%\begin{rSubsection}{Vanier Scholarship Nominee}{2016}{Nominated by Western University Faculty of Health Sciences}{}
%	\item ``The Vanier Canada Graduate Scholarships (Vanier CGS) was created to attract and retain world-class doctoral students and to establish Canada as a global centre of excellence in research and higher learning."
%\end{rSubsection}

%\begin{rSubsection}{Doctoral Research Award}{2016}{Canadian Institutes of Health Research}{}


\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
% Update to separate university publications & proceedings?
% Add DOIs

%%\newpage

\begin{rSection}{Publications}

% Journal articles
\begin{center}
	{\bf \emph{Journal Articles}}
\end{center}

\dagger\ denotes a student author

\begin{etaremune}

	\item {\bf Knowles, T.}, & Badh, G.\dagger\ (2022). The impact of face masks on spectral acoustics of speech: Effect of clear and loud speech styles. J. Acoust. Soc. Am., 11. DOI: 10.1121/10.0011400
	
	\item Badh, G.\dagger\, & {\bf Knowles, T.} (2022). Acoustic and perceptual impact of face masks on speech: A scoping review. OSF Preprints. https://doi.org/10.31219/osf.io/fpsu2

	\item Aveni, K.\dagger\, Ahmed, J., Borovsky, A., McRae, K., Jenkins, M., Sprengel, K., Fraser, J.A., Orange, J.B., {\bf Knowles, T.}, \& Roberts, A. (Accepted). Predictive language comprehension in Parkinson’s disease. \emph{PLOS ONE.}
% submitted at Cognition
% submitted at Cortex - rejected
% Cognitive Science presentation as well

	\item {\bf Knowles, T.}, Adams, S. G., \& Jog, M. (2021). Speech rate mediated vowel and stop voicing distinctiveness in Parkinson's disease. \emph{Journal of Speech, Language, and Hearing Research}, 64(11), 4096-4123. DOI: 10.1044/2021\_JSLHR-21-00160

	\item {\bf Knowles, T.}, Adams, S. G., \& Jog, M. (2021). Variation in speech intelligibility ratings as a function of speech rate modification in Parkinson's disease. \emph{Journal of Speech, Language, and Hearing Research}, 64(6), 1773-1793. DOI: 10.1044/2021\_JSLHR-20-00593

	\item {\bf Knowles, T.}, Adams, S. G., Page, A., Cushnie-Sparrow, D., \& Jog, M. (2020). A comparison of speech amplification and personal communication devices for hypophonia. \emph{Journal of Speech, Language, and Hearing Research}, 63(8), 2695-2712. DOI: 10.1044/2020\_JSLHR-20-00085
	
	\item Adams, S., Kumar, N., Rizek, P., Hong, A., Zhang, J., Abeyesekera, A., Mancinelli, C., {\bf Knowles, T.}, \& Jog, M. (2020). Efficacy and acceptance of a Lombard-response device for hypophonia in Parkinson’s disease. \emph{The Canadian Journal of Neurological Sciences}, 47(5), 634-641. DOI: 10.1017/cjn.2020.90

	\item Sonderegger, M., Stuart-Smith, J., {\bf Knowles, T.}, Macdonald, R., \& Rathcke, T. (2020). Structured heterogeneity in Scottish stops over the twentieth century. \emph{Language, 96}(1), 94-125. DOI: 10.1353/lan.2020.0003
	
	\item Abeyesekera, A., Adams, S., Mancinelli, C., {\bf Knowles, T.}, Gilmore, G., Delrobaei, M., Jog, M. (2019).  Effects of deep brain stimulation of the subthalamic nucleus settings on voice quality, intensity, and prosody in Parkinson’s disease: preliminary evidence for speech optimization. \emph{Canadian Journal of Neurological Sciences}, 46(3), 287-294. DOI: 10.1017/cjn.2019.16	

	\item {\bf Knowles, T.}, Clayards, M., \& Sonderegger, M. (2018). Examining factors influencing the viability of automatic acoustic analysis of child speech. \emph{Journal of Speech, Language, and Hearing Research}, 61(10), 2487-2501. DOI: 10.1044/2018\_JSLHR-S-17-0275.

	\item {\bf Knowles, T.}, Adams, S., Abeyesekera, A., Mancinelli, C., Gilmore, G., \& Jog, M. (2018). Deep brain stimulation of the subthalamic nucleus parameter optimization for vowel acoustics and speech intelligibility in Parkinson's disease. \emph{Journal of Speech, Language, and Hearing Research}, 61(3), 510-524. DOI: 10.1044/2017\_JSLHR-S-17-0157.

\end{etaremune}

% Proceedings
\begin{center}
	{\bf \emph{Proceedings \& Working Papers}}
\end{center}

\begin{etaremune}

	\item Cushnie-Sparrow, D., Adams, S.G., {\bf Knowles, T.}, Leszcz, T.M., Jog, M. (2016). Effects of multi-talker noise on the acoustics of voiceless stop consonants in Parkinson's disease. \emph{Western Papers in Linguistics.}

	\item {\bf Knowles, T.}, Clayards, M., Sonderegger, M., Wagner, M., Nadig, A., \& Onishi, K. (2015). Automatic forced alignment on child speech: Directions for improvement. \emph{Proceedings of Meetings on Acoustics.} DOI: 10.1121/2.0000125.

	\item Clayards, M. \& {\bf Knowles, T.} (2015). Prominence enhances voicelessness and not place distinction in English voiceless sibilants. \emph{Proceedings of the 18th International Congress of Phonetic Sciences.} Glasgow, UK: the University of Glasgow.

% Student working papers
	\item Little, C. \& {\bf Knowles, T.} (2012). Didja know? A comparative study of affrication across word boundaries in Canadian and American English. \emph{Strathy Student Working Papers on Canadian English.}

	\item Cheng, J. \& {\bf Knowles, T.} (2012). Mandarin VP-Shell: Not as hard as you think. \emph{McGill Cellar Door 1}, 4-20.

\end{etaremune}

\end{rSection}

%\newpage
% Manuscripts
\begin{rSection}{Manuscripts}

Page, A., Schroeder, J. R.\dagger, {\bf Knowles, T.}, Jog, M., \& Adams, S. (in revision). A comparison of voice amplifiers and personal communication systems for hypophonia:
An exploration of communicative participation.

{\bf Knowles, T.} \& Badh, G.\dagger\ (in revision). The impact of face masks on speech acoustics in Parkinson's disease: Effect of clear and loud speech styles.

Cline, N.\dagger\, \& {\bf Knowles, T.} (in prep). The impact of face masks on speech intelligibility and listener effort in Parkinson's disease: Effect of clear and loud speech styles.

{\bf Knowles, T.}, Cline, N.\dagger\, \& Parsa, V. (in prep). Controlled effects of face masks and shields on spectral acoustics, speech intelligibility, and listening effort.

Hassanpour, A.\dagger\, {\bf Knowles, T.}, \& Parsa, V. (in prep). Impact of masks on automatic speech recognition algorithm performance in noise.

{\bf Knowles, T.}, Adams, S.G., \& Jog, M. (in prep). Voice acoustics along a modified speech rate continuum in Parkinson's disease.


\end{rSection}


%----------------------------------------------------------------------------------------
%	CODE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publicly available code}
	Keshet, J., Sonderegger, M., \& {\bf Knowles, T.} (2014). AutoVOT, v. 0.94.
	\begin{itemize}
			\renewcommand\labelitemi{$\cdot$}
		\item A software package for automatic measurement of voice onset time (VOT), using the algorithm described in Sonderegger \& Keshet (2012).
		\item I maintain the README and the Praat plugin.
	\end{itemize}
	
	{\bf Knowles, T.} (unpublished). Publicly available Praat scripts.
	\begin{itemize}
			\renewcommand\labelitemi{$\cdot$}
		\item \url{https://github.com/thealk/PraatScripts}
		\item Includes Visual Analog Scale administration tool, interactive tutorials, and various scripts designed to facilitate speech analysis.
	\end{itemize}
	
\end{rSection}


%----------------------------------------------------------------------------------------
%	INVITED PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	REFEREED PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

%\newpage
\begin{rSection}{Presentations}

%\begin{rSection}{Invited Presentations}
%-----------------------------
% 		INVITED
%-----------------------------
\begin{center}
	{\bf \emph{Invited presentations}}
\end{center}

\begin{etaremune}

% ASHA Best practices 1 & 2

\item {\bf Knowles, T.} Speech amplification devices for hypophonia. SLP 625: Special Topics. Buffalo State University of New York, Buffalo, NY. 3/2021.

\item {\bf Knowles, T.} Speech acoustic adjustments along a speech rate continuum in Parkinson's disease. Rehabilitation Science Seminar. University at Buffalo, Buffalo, NY. 3/2020.

%\item {\bf Knowles, T.} Louder but not clearer: Exploring underpinnings of speech intelligibility in dysarthria through acoustic, clinical, and technological lenses. Job talk presented at the University of Minnesota Twin Cities. Minneapolis, MN. 1/2019.

%\item {\bf Knowles, T.} Louder but not clearer: Exploring underpinnings of speech intelligibility in dysarthria through acoustic, clinical, and technological lenses. Job talk presented at the University at Buffalo. Buffalo, NY. 11/2018.

\item {\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. A comparison of speech amplification and personal communication devices for individuals with Parkinson's disease. Communicative Disorders \& Sciences Research Colloquium. University at Buffalo, Buffalo, NY. 4/2018.

\end{etaremune}

%\end{rSection}

%-----------------------------
% 		REFEREED
%-----------------------------
\begin{center}
	{\bf \emph{Refereed conference presentations}}
	
	\emph{First author = presenter unless otherwise noted.}
\end{center}

\begin{etaremune}

% ASHA posters 2022

\item {\bf Knowles, T.}, \& Badh, G. The impact of face masks on speech acoustics in Parkinson's disease: Effect of clear and loud speech styles. 05/2022. Acoustical Society of America. Denver, CO. \emph{poster presentation.}

\item {\bf Knowles, T.}, \& Parsa, V. Controlled effects of face masks and shields on spectral acoustics, speech intelligibility, and listening effort. 02/2022. Motor Speech Conference. Charleston, SC. \emph{poster presentation.}

\item {\bf Knowles, T.}, Badh, G. The impact of face masks on spectral acoustics of speech: Effect of clear and loud speech styles. 02/2022. Motor Speech Conference. Charleston, SC. \emph{poster presentation.}

\item Hassanpour, A.,  Knowles, T., \& Parsa, V. Impact of masks on automatic speech recognition algorithm performance in noise. 01/2022. Speech in Noise Workshop (Virtual).

\item {\bf Knowles, T.}, Adams, S., \& Jog, M. Speech intelligibility in Parkinson's disease as a function of speech rate and task. 06/2021. International Clinical Phonetics and Linguistics Association Conference (Virtual). \emph{poster presentation.}

\item {\bf Knowles, T.}, Adams, S., \& Jog, M. Stop voicing contrasts in Parkinson's: Effect of modified speaking rate in connected speech. Boston Speech Motor Control Symposium. (Virtual) 06/2021. \emph{poster presentation.}

\item Aveni, K., Ahmed, J., Borovsky, A., McRae, K., Jenkins, M., Sprengel, K., Fraser, J.A., Orange, J.B., {\bf Knowles, T.}, Roberts, A. Predictive language comprehension in Parkinson’s disease. [Virtual poster]. Psychonomics Annual Meeting, Austin TX (Virtual), United States. 11/2020. \emph{poster presentation.}

\item  {\bf Knowles, T.}, Adams, S., \& Jog, M. VOT voicing distinction is robust along a speech rate continuum in dysarthria. Laboratory Phonology, Virtual, 07/2020.  \emph{poster presentation.}
   
\item {\bf Knowles, T.}, Adams, S., \& Jog, M. Acoustic changes along a modified speech rate continuum in Parkinson's disease. Motor Speech Conference. Santa Barbara, CA. 02/2020. \emph{poster presentation.}

\item {\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. Evaluating the efficacy of speech amplification and personal communication devices in Parkinson's disease. American Speech-Language-Hearing Association (ASHA) Conference. Boston, MA. 11/2018. \emph{poster presentation.}
	
\item {\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. A comparison of voice amplification devices in Parkinson's disease. 
		\begin{itemize}
			\renewcommand\labelitemi{$\cdot$}
			\item American Speech-Language-Hearing Association (ASHA) CONNECT Conference. Baltimore, MD. 7/2018 (new data presented). \emph{poster presentation.}
%			\item $5th$ Annual Movement Disorders Research Retreat. London, ON. 6/2018. \emph{Local oral presentation.}
			\item Speech-Language Pathology and Audiology Canada (SAC) Conference. Edmonton, AB. 5/2018. \emph{poster presentation.}
%			\item Health \& Rehabilitation  Graduate Research Conference. Western University, London, ON. 2/2018. \emph{Local oral presentation.}
		\end{itemize}
	
%	{\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. A comparison of speech amplifiers and personal communication systems for individuals with Parkinson's disease and hypophonia. 5th Annual Movement Disorders Research Retreat. London, ON. 6/2018. \emph{Local oral presentation.}

%	{\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. Comparison of speech amplification devices in individuals with Parkinson's disease. Speech-Language Pathology and Audiology Canada (SAC) Conference. Edmonton, AB. 5/2018. \emph{National poster presentation.} 
	
%	{\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. A comparison of speech amplification devices in individuals with Parkinson's disease. Health \& Rehabilitation  Graduate Research Conference. Western University, London, ON. 2/2018. \emph{Local oral presentation.}
	
%	{\bf Knowles, T.} The effect of rate manipulation on acoustic distinctiveness and intelligibility in dysarthria: Prospectus. 
%	\begin{itemize}
%		\renewcommand\labelitemi{$\cdot$}
%		\item Speech \& Language Seminar, Health \& Rehabilitation Sciences, Western University. London, ON. 10/2017. \emph{Local oral presentation.}
%		\item $4th$ Annual Movement Disorders Research Retreat. London, ON. 6/2017. \emph{Local oral presentation.}
%	\end{itemize}
%	
%%	{\bf Knowles, T.} The effect of rate manipulation on acoustic distinctiveness and intelligibility in dysarthria: Prospectus. 4th Annual Movement Disorders Research Retreat. London, ON. 6/2017. \emph{Local oral presentation.}
%	
%	{\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Gilmore, G., \& Jog, M. Deep brain stimulation parameter optimization: Vowel acoustics in Parkinson's disease. Health \& Rehabilitation Graduate Research Conference. Western University, London, ON. 2/2017. \emph{Local oral presentation.}
	
\item Mancinelli, C., Adams, S.G., Abeyesekera, A., {\bf Knowles, T.}, Delrobaei, M., \& Jog, M. Deep brain stimulation parameter optimization for rate of speech in Parkinson's disease. American Speech-Language-Hearing Association Convention. Philadelphia, PA. 11/2016. \emph{poster presentation.}
	
\item {\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., \& Jog, M. Deep brain stimulation parameter optimization for speech intelligibility and vowel acoustics in Parkinson's disease. International Clinical Phonetics and Linguistics Association Conference, Halifax, NS. 6/2016. \emph{oral presentation.}
	
\item Abeyesekera, A., Adams, S.G., {\bf Knowles, T.}, Mancinelli, C., Delrobaei, M., \& Jog, M. Deep brain stimulation and speech in Parkinson's disease: Effects of stimulator settings and electrode contact positions. Southern Ontario Neuroscience Association, Waterloo, ON. 5/2016. \emph{poster presentation.}
	
%	Cushnie-Sparrow, D., Adams, S.G., Leszcz, T., {\bf Knowles, T.},  \& Jog., M. Effects of multitalker noise on the acoustics of voiceless stop consonants in Parkinson disease. Western Interdisciplinary Student Symposium on Language Research, London, ON. 3/2016. \emph{Local oral presentation.}
	% Accepted but did not attend: 9th annual Toronto Undergraduate Linguistics Conference, Toronto, ON. 3/2016.
	
	
\item {\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Delrobaei, \& M., Jog., M. Deep brain stimulation parameter optimization for speech intelligibility and speech acoustics in Parkinson's disease. Motor Speech Conference, Newport Beach, CA. 3/2016. \emph{poster presentation.}
	
\item Abeyesekera, A., Adams, S.G., {\bf Knowles, T.}, Mancinelli, C., Delrobaei, \& M., Jog., M. Deep brain stimulation parameter optimization for voice quality, speech intensity and prosody of speech in Parkinson's disease. Motor Speech Conference, Newport beach, CA. 3/2016. \emph{poster presentation.}
	
%	{\bf Knowles, T.}, Adams, S., Leszcz, T., Jog, M. Acoustic correlates of noise-related speech intelligibility deficits in Parkinson?s disease. Health and Rehabilitation Sciences Graduate Research Conference. Western University, London, ON. 2/2016. \emph{Local oral presentation.}
	
\item {\bf Knowles, T.}, Clayards, M., Sonderegger, M., Wagner, M., Nadig, A., \& Onishi, K. Automatic forced alignment on child speech: Directions for improvement. Meeting of the Acoustical Society of America, Jacksonville, FL. 11/2015. \emph{poster presentation.}
	
%	{\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Delrobaei, \& M., Jog., M. Deep brain stimulation and speech.
%	\begin{itemize}
%				\renewcommand\labelitemi{$\cdot$}
%		\item $3rd$ Annual Movement Disorders Research Retreat. Toronto, ON. 6/2016.  \emph{Local oral presentation.}
%		\item $2nd$ Annual Movement Disorders Research Retreat. London, ON. 6/2015.  \emph{Local oral presentation.}
%	\end{itemize}
%	
%	{\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Delrobaei, \& M., Jog., M. Effect of deep brain stimulation parameters on speech intelligibility and speech acoustics in Parkinson's disease. 
%	\begin{itemize}
%				\renewcommand\labelitemi{$\cdot$}
%		\item Health \& Rehabilitation Sciences Graduate Research Conference. Western University, London, ON.  2/2015.  \emph{Local poster presentation.}
%		\item Faculty of Health Sciences Research Day. Western University, London, ON. 3/2015.  \emph{Local poster presentation.}
%	\end{itemize}
%	
%	Abeyesekera, A., Adams, S., {\bf Knowles, T.}, Mancinelli, C., Delrobaei, M., \& Jog, M. Effect of different deep brain stimulation parameters on voice quality, speech intensity, and prosody in Parkinson's Disease. Health \& Rehabilitation Sciences Graduate Research Conference, Western University, London, ON. 2/2015.  \emph{Local poster presentation.}
%	
%	Mancinelli, C., Adams, S., Abeyesekera, A., {\bf Knowles, T.}, Delrobaei, M., \& Jog, M. Deep brain stimulation parameter optimization for rate of speech in Parkinson's Disease. Health \& Rehabilitation Sciences Graduate Research Conference, Western University, London, ON. 2/2015. \emph{Local poster presentation.}
	
\item Sonderegger, M., Stuart-Smith, J., Macdonald, R., {\bf Knowles, T.}, \& Rathcke, T. Stability and change in Scottish stops: A real-time study of three acoustic cues in Glaswegian vernacular. New Ways of Analyzing Variation 44, Toronto. 10/2015. \emph{oral presentation.}
	
\item Clayards, M., \& {\bf Knowles, T.} Prominence enhances voicelessness and not place distinction in English voiceless sibilants. 18th International Congress of Phonetic Sciences. Glasgow, Scotland. 8/2015. \emph{International oral presentation.}
	
\item Stuart-Smith, J., Sonderegger, M., Macdonald, R., {\bf Knowles, T.}, \& Rathcke, T. (2014). The private life of stops: VOT in a real-time corpus of spontaneous Glaswegian. 14th Conference on Laboratory Phonology. Tokyo, Japan. 7/2014. \emph{oral presentation.}
	
\item Clayards, M., \& {\bf Knowles, T.} Sibilants, prominence, contrast and breathy voice. Phonetic Building Blocks of Speech. University of Victoria. Victoria, BC. 9/2014. \emph{poster presentation.}
	
%	Clayards, M., Wonnacott, E., \& {\bf Knowles, T.} A case study of childhood L2 learning of phonological contrasts. McGill School of Communication Sciences and Disorders 50th Anniversary Open House. McGill University. Montr\'eal, QC. 11/2013. \emph{Local poster presentation.}
	
\item Clayards, M. \& {\bf Knowles, T.} Prosodic strengthening and sibilants. Linguistic Institute Conference on Universality and Variability in segment-prosody interactions. Ann Arbor, MI. 6/2013. \emph{oral presentation.}
	
\item Fleischer, D., {\bf Knowles, T.}, Cheng, J., Wagner, M., \& Clayards, M. Syntactic effects on compensation for assimilation. Architectures and Mechanisms for Language Processing. Riva del Garda, Italy. 9/2012. \emph{oral presentation.}
	
\item Little, C. \& {\bf Knowles, T.} Didja Know? Affrication in North American English Dialects.
	\begin{itemize}
				\renewcommand\labelitemi{$\cdot$}
		\item Change and Variation in Canada 7. University of Toronto. Toronto, ON. 5/2012. \emph{joint oral presentation.}
		\item 2nd Annual Hunter Undergraduate Linguistics and Language Study. Hunter College. New York, NY. 5/2012. \emph{oral presentation.}
		\item International Linguistic Assoc. 58th Annual Conference. Kingsborough Community College. Brooklyn, NY. 4/2012. \emph{joint oral presentation.}
		\item 10th Annual Harvard Undergraduate Linguistics Colloquium. Harvard University. Cambridge, MA. 4/2012. \emph{joint oral presentation.}
	\end{itemize}
	
\item {\bf Knowles, T.} (2011). Gender and Lexical Variation: Coffee Tasting Descriptors. 
	\begin{itemize}
				\renewcommand\labelitemi{$\cdot$}
		\item McGill Canadian Conference for Linguistics Undergraduates. Montr\'eal, QC. 3/2011. \emph{oral presentation.}
		\item 9th Annual Harvard Undergraduate Linguistics Colloquium. Harvard University. Cambridge, MA. \emph{oral presentation.}
	\end{itemize}

%\end{rSection}
\end{etaremune}




%-----------------------------
% 		LOCAL
%-----------------------------
\begin{center}
	{\bf \emph{Local presentations}}
\end{center}

\begin{etaremune}

\item {\bf Knowles, T.} Speech amplification clinic: Speech-language pathology in-service. H.A. Leeper Speech \& Hearing Clinic. Western University, London, ON. 1/2019.

\item {\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. Evaluating the efficacy of voice amplification and personal communication devices in Parkinson's disease. Speech \& Language Seminar, Health \& Rehabilitation Sciences, Western University. London, ON. 10/2018. \emph{Local oral presentation.}

\item {\bf Knowles, T.}, Adams, S., Page, A., Cushnie-Sparrow, D., \& Jog, M. A comparison of voice amplification devices in Parkinson's disease. 
		\begin{itemize}
			\renewcommand\labelitemi{$\cdot$}
%			\item American Speech-Language-Hearing Association (ASHA) CONNECT Conference. Baltimore, MD. 7/2018 (new data presented). \emph{International poster presentation.}
			\item $5th$ Annual Movement Disorders Research Retreat. London, ON. 6/2018. \emph{Local oral presentation.}
%			\item Speech-Language Pathology and Audiology Canada (SAC) Conference. Edmonton, AB. 5/2018. \emph{National poster presentation.}
			\item Health \& Rehabilitation  Graduate Research Conference. Western University, London, ON. 2/2018. \emph{Local oral presentation.}
		\end{itemize}
		
\item {\bf Knowles, T.} The effect of rate manipulation on acoustic distinctiveness and intelligibility in dysarthria: Prospectus. 
	\begin{itemize}
		\renewcommand\labelitemi{$\cdot$}
		\item Speech \& Language Seminar, Health \& Rehabilitation Sciences, Western University. London, ON. 10/2017. \emph{Local oral presentation.}
		\item $4th$ Annual Movement Disorders Research Retreat. London, ON. 6/2017. \emph{Local oral presentation.}
	\end{itemize}
	
	
\item {\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Gilmore, G., \& Jog, M. Deep brain stimulation parameter optimization: Vowel acoustics in Parkinson's disease. Health \& Rehabilitation Graduate Research Conference. Western University, London, ON. 2/2017. \emph{Local oral presentation.}

	Cushnie-Sparrow, D., Adams, S.G., Leszcz, T., {\bf Knowles, T.},  \& Jog., M. Effects of multitalker noise on the acoustics of voiceless stop consonants in Parkinson disease. Western Interdisciplinary Student Symposium on Language Research, London, ON. 3/2016. \emph{Local oral presentation.}

\item {\bf Knowles, T.}, Adams, S., Leszcz, T., Jog, M. Acoustic correlates of noise-related speech intelligibility deficits in Parkinson's disease. Health and Rehabilitation Sciences Graduate Research Conference. Western University, London, ON. 2/2016. \emph{Local oral presentation.}
	
\item {\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Delrobaei, \& M., Jog., M. Deep brain stimulation and speech.
	\begin{itemize}
				\renewcommand\labelitemi{$\cdot$}
		\item $3rd$ Annual Movement Disorders Research Retreat. Toronto, ON. 6/2016.  \emph{Local oral presentation.}
		\item $2nd$ Annual Movement Disorders Research Retreat. London, ON. 6/2015.  \emph{Local oral presentation.}
	\end{itemize}
	
\item {\bf Knowles, T.}, Adams, S.G., Abeyesekera, A., Mancinelli, C., Delrobaei, \& M., Jog., M. Effect of deep brain stimulation parameters on speech intelligibility and speech acoustics in Parkinson's disease. 
	\begin{itemize}
				\renewcommand\labelitemi{$\cdot$}
		\item Health \& Rehabilitation Sciences Graduate Research Conference. Western University, London, ON.  2/2015.  \emph{Local poster presentation.}
		\item Faculty of Health Sciences Research Day. Western University, London, ON. 3/2015.  \emph{Local poster presentation.}
	\end{itemize}
	
\item Abeyesekera, A., Adams, S., {\bf Knowles, T.}, Mancinelli, C., Delrobaei, M., \& Jog, M. Effect of different deep brain stimulation parameters on voice quality, speech intensity, and prosody in Parkinson's Disease. Health \& Rehabilitation Sciences Graduate Research Conference, Western University, London, ON. 2/2015.  \emph{Local poster presentation.}
	
\item Mancinelli, C., Adams, S., Abeyesekera, A., {\bf Knowles, T.}, Delrobaei, M., \& Jog, M. Deep brain stimulation parameter optimization for rate of speech in Parkinson's Disease. Health \& Rehabilitation Sciences Graduate Research Conference, Western University, London, ON. 2/2015. \emph{Local poster presentation.}

\item Clayards, M., Wonnacott, E., \& {\bf Knowles, T.} A case study of childhood L2 learning of phonological contrasts. McGill School of Communication Sciences and Disorders 50th Anniversary Open House. McGill University. Montr\'eal, QC. 11/2013. \emph{Local poster presentation.}

\end{etaremune}
\end{rSection}



%\newpage
%----------------------------------------------------------------------------------------
%	MEDIA SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Media}
%\begin{itemize}
%	\renewcommand\labelitemi{$\cdot$}
%	\item ``Speech in Parkinson's disease: The potential role of amplification devices.'' Article written for \textit{The Parkinson's Update (68).} Parkinson Society Southwestern Ontario. Online. Summer/Fall 2018. \url{https://parkinsonsociety.ca/wp-content/uploads/2018/07/Parkinson-68-complete-for-web-Compressed-003-final.pdf}
%	\item``The R-Ladies Piece.'' Interview by GradCast for \textit{Radio Western.} Radio. 6/2017.
%	\item ``Research fine-tunes Parkinson's speech impact.'' Interview by Paul Mayne for \textit{Western News.} Online. 3/2016. \url{https://news.westernu.ca/2016/03/research-fine-tunes-parkinsons-speech-impact/}
%\end{itemize}

{\bf ``Speech in Parkinson's disease: The potential role of amplification devices.''} Article written for \textit{The Parkinson's Update (68).} Parkinson Society Southwestern Ontario. Online. Summer/Fall 2018. \url{https://parkinsonsociety.ca/wp-content/uploads/2018/07/Parkinson-68-complete-for-web-Compressed-003-final.pdf}

{\bf ``The R-Ladies Piece.''} Interview by GradCast for \textit{Radio Western.} Radio. 6/2017.

{\bf ``Research fine-tunes Parkinson's speech impact.''} Interview by Paul Mayne for \textit{Western News.} Online. 3/2016. \url{https://news.westernu.ca/2016/03/research-fine-tunes-parkinsons-speech-impact/}

\end{rSection}

%%\newpage


%
%%----------------------------------------------------------------------------------------
%%	HONOURS & AWARDS SECTION
%%----------------------------------------------------------------------------------------
%
%\begin{rSection}{Honours \& Awards}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Summer)}{2018}{Western University Society of Graduate Students}{}
%\item Value: \$500.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2018}{Western University Faculty of Health Sciences}{}
%\item Value: \$250.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Spring)}{2018}{Western University Society of Graduate Students}{}
%\item Value: \$300.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Teaching Award Nominee (not awarded)}{2018}{Western University}{}
%\end{rSubsection}
%
%\begin{rSubsection}{Ontario Graduate Scholarship}{2018-2019}{}{}
%\item Value: \$15,000
%\end{rSubsection}
%
%\begin{rSubsection}{Ontario Graduate Scholarship}{2017-2018}{}{}
%\item Value: \$15,000
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Research Program Award}{2017-2018}{Parkinson Society Southwestern Ontario}{}
%\item Value: \$20,000
%\end{rSubsection}
%
%\begin{rSubsection}{Vanier Scholarship Nominee (not awarded)}{2016}{Nominated by Western University Faculty of Health Sciences}{}
%\end{rSubsection}
%
%\begin{rSubsection}{Western University ``3 Minute Thesis'' First Place Winner}{2016}{Western University}{}
%\item  Value: \$1,000
%\end{rSubsection}
%
%\begin{rSubsection}{Harmonize for Speech Graduate Student Award}{2016}{Harmonize for Speech Ontario}{}
%\item Value: \$750
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Spring)}{2016}{Western University Society of Graduate Students}{}
%\item Value: \$500.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2016}{Western University Health \& Rehabilitation Sciences}{}
%\item Value: \$400.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2016}{Western University Faculty of Health Sciences}{}
%\item Value: \$300.00
%\end{rSubsection}
%
%\begin{rSubsection}{Student Achievement Award}{2015}{Ontario Association of Speech-Language Pathologists \&
%Audiologists}{}
%\item Value: OSLA Membership
%\end{rSubsection}
%
%\begin{rSubsection}{Acoustical Society of America Student Poster Honorable Mention}{2015}{Meeting of the 170th Acoustical Society of America, Jacksonville}{}
%\end{rSubsection}
%
%\begin{rSubsection}{Best PhD Student Poster Award}{2015}{Health \& Rehabilitation Sciences Graduate Research Conference, Western University}{}
%\end{rSubsection}
%
%%\begin{rSubsection}{Western Graduate Research Scholarship}{2014, 2015, 2016}{Value: \$19,000 annually}{} %Current value: \$19,000 annually}{}
%%\end{rSubsection}
%
%\begin{rSubsection}{Graduation with First Class Honours \& Distinction}{2012}{McGill University}{ }
%\end{rSubsection}
%
%\begin{rSubsection}{Dean's Honour List}{2010}{McGill University}{}
%\end{rSubsection}
%
%
%\end{rSection}

%%\newpage

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
% 	RESEARCH
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience: Research}


	\begin{rSubsection}{Lab Director: Clinical Applications of Speech Acoustics (CASA) Lab}{2022 - present}{Communicative Sciences \& Disorders, Michigan State University}{East Lansing, MI}
	\end{rSubsection}
	
	\begin{rSubsection}{Lab Director: Clinical Applications of Speech Acoustics (CASA) Lab}{2019 - 2022}{Communicative Disorders \& Sciences, University at Buffalo}{Buffalo, NY}
	\end{rSubsection}

	\begin{rSubsection}{Research Assistant}{November 2014 - August 2019}{Speech Movement Disorders Lab, Western University}{London, ON}
	\item Assist with study design, ethics submission, data collection related to a comparison of assistive speech devices for individuals with Parkinson's disease
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Lab Coordinator/Research Assistant}{October 2014 - June 2017}{Language \& Cognition Lab, Western University}{London, ON}
	\item Assist with study design, ethics proposals, recruitment, data collection/analysis related to language comprehension in Parkinson's disease
	\item Manage research assistants, coordinate meetings, ensure project deadlines are met
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Project Manager: Tools for Looking at Variability in Speech}{August 2013 - June 2014}{McGill University}{Montr\'eal, QC}
	\item Multidisciplinary collaboration with Communication Sciences \& Disorders, Linguistics, \& Psychology investigating viability of automated analysis with large scale variable speaker populations
	\item Trained \& managed 12+ research assistants in speech analysis
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Lab Manager: Speech Learning Lab}{August 2013 - June 2014}{Linguistics Department, McGill University}{Montr\'eal, QC}
	\item Trained \& managed research assistants in acoustic analysis
	\item Provided training materials and conducted tutorial on Praat scripting
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Lab Manager: Montr\'eal Language Modeling Lab}{June 2013 - June 2014}{Linguistics Department, McGill University}{Montr\'eal, QC}
	\item Developed automated scripts for speech analysis, performed data collection \& acoustic analysis
	\item Trained \& managed research assistants \& coordinated meetings
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Research Assistant: CHILDES PhonBank Project}{September 2012 - March 2014}{Linguistics Department, McGill University}{Montr\'eal, QC}
	\item Edited and maintained corpus of child phonological data
	\item Provided detailed feedback for ongoing development of PhonBank software
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Research Assistant: McGill Prosody Lab}{June 2012 - June 2014}{Linguistics Department, McGill University}{Montr\'eal, QC}
	\item Performed data collection for a variety of speech production and perception experiments
	\item Assisted in data analysis using MatLab and Praat software
	\end{rSubsection}
	
	%------------------------------------------------
	
	\begin{rSubsection}{Research Assistant: Speech Learning Lab}{November 2011 - June 2014}{Linguistics Department, McGill University}{Montr\'eal, QC}
	\item Assisted in speech perception and production experimental design
	\item Conducted acoustic and statistical analysis
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
% 	CLINICAL
%----------------------------------------------------------------------------------------

%%\newpage
\begin{rSection}{Professional Experience: Clinical}

	\begin{rSubsection}{Speech-language pathologist (Clinical Fellowship)}{November 2019 - June 2022}{UB Speech and Hearing Clinic}{Buffalo, NY}
	\item Lead SPEAK OUT!\textregistered \ and LOUD Crowd\textregistered \ therapy sessions for people with Parkinson's disease.
	\end{rSubsection}
%
%	\begin{rSubsection}{Student Clinician: Hospital}{July 2019 - August 2019}{Grand River Hospital}{Kitchener, ON}
%	\item Provided swallowing and communication assessments on a stroke unit.
%	\end{rSubsection}
%
%	\begin{rSubsection}{Student Clinician: Speech Amplification Clinic}{September 2018 - June 2019}{H.A. Leeper Speech \& Hearing Clinic}{London, ON}
%	\item Developed policies and procedures for and led assessments of individuals with hypophonia seeking a speech amplification device
%	\item Coordinated meetings with speech-language pathologists, audiologists, neurologists and clinic staff to ensure timely prescription of appropriate devices
%	\end{rSubsection}
%
%	\begin{rSubsection}{Student Clinician: Schoolboard}{May 2018 - June 2018}{Thames Valley District Schoolboard}{London, ON}
%	\item Conducted assessment and intervention for school-aged children
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Student Clinician: Fluency disorders}{August 2017}{Camp ShoutOut}{Holton, MI, USA.}
%	\item Provided individual and group intervention to children with fluency disorders
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Student Clinician: Acquired neurogenic language disorders}{May 2015 - July 2015}{H.A. Leeper Speech \& Hearing Clinic}{London, ON}
%	\item Conducted assessment and intervention for adults with aphasia
%	\item Provided individual \& group therapy
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Student Clinician: Voice disorders}{May 2015 - June 2015}{H.A. Leeper Speech \& Hearing Clinic}{London, ON}
%	\item Delivered LSVT-LOUD to client with Parkinson's disease
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Student Clinician: TykeTalk}{January 2015 - April 2015}{H.A. Leeper Speech \& Hearing Clinic}{London, ON}
%	\item Conducted assessment and intervention for young children with suspected speech and/or language difficulties
%	\item Assisted in providing Hanen Target Word intervention
%	\end{rSubsection}
\end{rSection}
%------------------------------------------------

%%------------------------------------------------
%% NOT FOR ACADEMIC CV
%%------------------------------------------------
%
%\begin{rSubsection}{Tutor}{September 2011 - August 2013}{Private family}{Montr\'eal, QC}
%\item Provided math, English, and French homework help to a child with dyslexia
%\end{rSubsection}
%
%%------------------------------------------------
%
%\begin{rSubsection}{Director of Quality Control}{October 2008 - October 2012}{Cafe Myriade}{Montr\'eal, QC}
%\item Trained new staff in specialty coffee brewing and customer service
%\item Maintained high standard of quality in extremely high-paced environment
%\item Conducted routine coffee tastings and brewing methodology calibration to assess product quality
%\end{rSubsection}
%
%%------------------------------------------------
%\begin{rSubsection}{Waitress}{October 2006 - August 2007}{Esselon Cafe}{Hadley, MA}
%\item Provided exceptional customer service in extremely fast-paced \& quality-driven environment
%\item Waited on tables, took orders, checked and stocked inventory
%\end{rSubsection}
%%------------------------------------------------
%
%\begin{rSubsection}{Rock climbing course developer and instructor}{October 2005 - July 2007}{Northampton Athletic Club}{Northampton, MA}
%\item Developed weekly rock climbing program and summer camp for children ages 4 to 13
%\item Instructed children ages 4 to 13 on rock climbing technique and safety
%\end{rSubsection}
%%------------------------------------------------
%
%\begin{rSubsection}{Rock wall desk supervisor}{October 2005 - July 2007}{Northampton Athletic Club}{Northampton, MA}
%\item Supervised rock wall customers, ensured safety and hygiene standards were maintained, conducted regular beginner climbing sessions and safety classes
%\end{rSubsection}

%\end{rSection}



%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
	%\begin{rSubsection}{Teaching Assistant: Speech Science (COMMSCI9625)}{Fall 2017}{Communication Sciences \& Disorders}{Western University}
	%\item Delivered lecture: \emph{Introduction to phonetics}
	%\item Conducted three weekly labs on healthy and disordered speech acoustics
	%\end{rSubsection}

%%%%%%%%%%%%%
\begin{center}
	{\bf \emph{Instructor}}
\end{center}
	\begin{rSubsection}{Research Methods (CSD803)}{Fall 2022}{Michigan State University, Department of Communicative Sciences \& Disorders}{co-taught}
	\end{rSubsection}
	
	\begin{rSubsection}{Anatomy and Physiology of the Speech Mechanism (CSD213)}{Fall 2022}{Michigan State University, Department of Communicative Sciences \& Disorders}{}
	\end{rSubsection}

	\begin{rSubsection}{Data Analytics for Speech, Language, and Hearing Sciences (CDS491/687)}{Spring 2022}{University at Buffalo, Department of Communicative Disorders \& Sciences}{}
	\end{rSubsection}

	\begin{rSubsection}{Motor Speech Disorders (CDS640)}{Fall 2020, 2021}{University at Buffalo, Department of Communicative Disorders \& Sciences}{co-taught}
	\end{rSubsection}
	
	\begin{rSubsection}{Anatomy and Physiology of the Speech Mechanism (CDS288)}{Fall 2019, 2020, 2021}{University at Buffalo, Department of Communicative Disorders \& Sciences}{}
	\end{rSubsection}

%%%%%%%%%%%%%
\begin{center}
	{\bf \emph{Teaching Assistant}}
\end{center}
	
	\begin{rSubsection}{Speech Science (COMMSCI9615)}{Fall 2016, 2017}{Western University, School of Communication Sciences \& Disorders}{}
	\item Conducted three weekly labs on healthy and disordered speech acoustics for graduate SLP and Audiology students
	\end{rSubsection}

	\begin{rSubsection}{Voice Disorders (COMMSCI9631)}{Spring 2017}{Western University, School of Communication Sciences \& Disorders}{}
	\item Graded quizzes and exams related to healthy and disordered voice production for graduate SLP students
	\end{rSubsection}
	
	
%%%%%%%%%%%%%
\begin{center}
	{\bf \emph{Guest Lectures}}
\end{center}
	\begin{rSubsection}{``Introduction to dysarthria"}{October 2022.}{Introduction to Communicative Sciences \& Disorders (CSD203)}{Michigan State University}
	\end{rSubsection}

	\begin{rSubsection}{``So you're thinking about graduate school for communication disorders?"}{December 2020.}{Syntax 1 (LING371)}{McGill University}
	\end{rSubsection}

	\begin{rSubsection}{``Introduction to phonetics"}{September 2017, 2018}{Speech Science (COMMSCI9615)}{Western University}
	\end{rSubsection}

	\begin{rSubsection}{``Treatment trends in hypokinetic dysarthria'' }{March 2018}{Motor Speech Disorders (SLP714)}{Central Michigan University}
	\end{rSubsection}
	
	\begin{rSubsection}{``Pursuing a PhD in communication sciences and disorders''}{November 2017}{Professional Practice Issues (COMMSCI9636)}{Western University}
	\end{rSubsection}

%%\newpage
%%%%%%%%%%%%%
\begin{center}
		{\bf \emph{Workshops \& tutorials}}
\end{center}

	\begin{rSubsection}{``Intro to RMarkdown"}{March 2021}{R-Ladies, Coventry UK Chapter}{}
	\end{rSubsection}

	\begin{rSubsection}{Praat Scripting Workshops}{Spring 2021}{Department of Communicative Disorders \& Sciences}{University at Buffalo}
		\item Regular workshops (every 3 weeks) to introduce students from CDS, Linguistics, and Cognitive Science to programming in the Praat acoustic analysis software.
		\item I organize the workshops and facilitated two. Some of the students in my lab are required to learn these skills and we build on them at our biweekly lab meetings as well.
	\end{rSubsection}

	\begin{rSubsection}{Coding for Speech}{Spring 2020}{Department of Communicative Disorders \& Sciences}{University at Buffalo}
		\item Weekly workshops on using tools to analyze speech data, given to students and faculty at the University at Buffalo and led by me.
		\item Terminated after 2 sessions due to COVID19 pandemic
	\end{rSubsection}

	\begin{rSubsection}{``RMarkdown and Bookdown for academic writing"}{January 2020}{R-Ladies, London, Ontario Chapter}{}
	\end{rSubsection}

	\begin{rSubsection}{``Dissertating with RMarkdown and Bookdown"}{April 2019}{R-Ladies, London, Ontario Chapter}{}
	\end{rSubsection}
%	\item Conducted interactive presentation and tutorial on using the programming language and software environment R to write a dissertation	
%	\end{rSubsection}
	
	\begin{rSubsection}{``Figuring out figures in R"}{October 2018}{R-Ladies, London, Ontario Chapter}{}
%	\item Conducted interactive presentation and tutorial on using the programming language and software environment R to explore data and generate customized visualizations using the ggplot package
	\end{rSubsection}
	
	
	\begin{rSubsection}{``Using RMarkdown to generate reports and manuscripts"}{March 2018}{R-Ladies, London, Ontario Chapter}{}
%	\item Conducted interactive presentation and tutorial on using the programming language and software environment R to produce integrated reports and manuscripts
	\end{rSubsection}
	
	
	\begin{rSubsection}{``Introduction to Praat Scripting"}{Spring 2014}{Department of Linguistics}{McGill University}
		\item Conducted tutorials for various linguistics laboratory research assistants on automating aspects of acoustic analysis by writing scripts in Praat
	\end{rSubsection}

\end{rSection}




%----------------------------------------------------------------------------------------
%	ACADEMIC SERVICE SECTION
%----------------------------------------------------------------------------------------

%\begin{center}
%	{\bf \emph{Other Service \& Leadership}}
%\end{center}

%\begin{itemize}
%	\item Co-founder, R-Ladies London, Ontario Chapter (2017 - 2019)
%	\item Chair/Organizer, Health \& Rehabilitation Sciences Alumni Speaker Series, Western University (2016 - 2017)
%	\item Sponsorship Subcommittee Leader, Health \& Rehabilitation Sciences Graduate Research Conference, Western University (2016 - 2017)
%	\item Vice-President Finance, Health \& Rehabilitation Sciences Graduate Student Society, Western University (2016 - 2017)
%	\item President, Health \& Rehabilitation Sciences Graduate Student Society, Western University (2015 - 2016)
%	\item Conference organizer, Health \& Rehabilitation Sciences Graduate Research Conference, Western University (2015, 2016)
%	\item Conference abstract reviewer, Health \& Rehabilitation Sciences Graduate Research Conference, Western University (2015, 2016)
%	\item Professional Program Preview Day Volunteer, School of Communication Sciences \& Disorders, Western University (2015)
%\end{itemize}

\begin{rSection}{Academic Service \& Leadership}

%----------------------------------------------------------------------------------------
%	ADVISING SECTION
%----------------------------------------------------------------------------------------
\bigskip
\begin{center}
	{\bf \emph{Advising}}\\
\end{center}

\begin{rSubsection}{MA Thesis Committees}{}{University at Buffalo, Department of Communicative Disorders \& Sciences}{}
	\item Francesca D'Alessandro. \emph{Impact of Vocal Hygienic Advice on the Voice of University Lecturers (2021)}.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROFESSION SERVICE
%----------------------------------------------------------------------------------------
\bigskip
\begin{center}
	{\bf \emph{Service to the Profession}}\\
\end{center}

\begin{rSubsection}{Journal Article Reviews}{}{}{}
	\item \emph{American Journal of Speech Language Pathology}
	\item \emph{Journal of Speech, Language, and Hearing Research}
	\item \emph{International Journal of Language and Communication Disorders}
\end{rSubsection}


\begin{rSubsection}{Conference Planning \& Abstract Review}{}{}{}
	\item America Speech-Language and Hearing Association Convention: Speech and Language Science Subcommittee (2021, 2022)
	\item Western University Health \& Rehabilitation Sciences Graduate Research Conference (2015, 2016)
\end{rSubsection}



%----------------------------------------------------------------------------------------
%	DEPT SERVICE SECTION
%----------------------------------------------------------------------------------------
%\newpage
\begin{center}
	{\bf \emph{Service to the Department}}\\
%	{\emph{University at Buffalo, Department of Communicative Disorders \& Sciences}
\end{center}

%\begin{itemize}
%	\item Subcommittee Leader for Departmental SWOT Analysis - Speech
%	\item Search Committee Member for Assistant Professor (2019)
%	\item Subcommittee Member for Speech Equipment Funds (2019)
%\end{itemize}

% included director in general, since not really service to the dept...
%	\begin{rSubsection}{Lab Director: Clinical Applications of Speech Acoustics (CASA) Lab}{2019 - Present}{}{}
%	\end{rSubsection}

\begin{rSubsection}{Communicative Disorders \& Sciences}{}{University at Buffalo}{}
	\item Member of graduate admissions committee; Spring 2022
	\item Member of search committee for Assistant/Associate Professor; Winter 2022
	\item Member of Coalition for Anti-Racism \& Equity; Summer 2020 - Spring 2022
	\item Member of search committee for Clinical Assistant/Associate Professor; Fall 2020
	\item Leader of subcommittee departmental SWOT analysis; Winter 2020
	\item Member of search committee for Assistant Professor; Fall 2019
\end{rSubsection}

%	\begin{rSubsection}{Member of Coalition for Anti-Racism \& Equity}{Summer 2020 - Present}{}{}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Member of search committee for Clinical Assistant/Associate Professor}{Fall 2020}{}{}
%	\end{rSubsection}
%
%	\begin{rSubsection}{Leader of subcommittee departmental SWOT analysis}{Winter 2020}{}{}
%	\end{rSubsection}
%
%	\begin{rSubsection}{Member of search committee for Assistant Professor}{Fall 2019}{}{}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Member of subcommittee for Speech Equipment Funds}{Fall 2019}{}{}
%	\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Graduate student SERVICE SECTION
%----------------------------------------------------------------------------------------
%\bigskip
%%\newpage
%\begin{center}
%	{\bf \emph{Service as Graduate Student}}\\
%\end{center}
%
%\begin{rSubsection}{Health \& Rehabilitation Sciences Graduate Student Society}{}{Western University}{}
%	\item Chair/Organizer: Alumni Speaker Series; 2016 --- 2017
%	\item Leader of Sponsorship Subcommittee for Graduate Research Conference; 2016 --2017
%	\item Vice-President Finance; 2016 --- 2017
%	\item President; 2015 --- 2016
%	\item Co-Organizer: Graduate Research Conference; 2016
%	\item Professional Program Preview Day Volunteer (School of Communication Sciences \& Disorders); 2015
%\end{rSubsection}

%	\begin{rSubsection}{Chair/Organizer}{2016 --- 2017}{Health \& Rehabilitation Sciences Alumni Speaker Series}{Western University}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Sponsorship Subcommittee Leader}{2016 --- 2017}{Health \& Rehabilitation Sciences Graduate Research Conference}{Western University}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Vice-President Finance}{2016 --- 2017}{Health \& Rehabilitation Sciences Graduate Student Society}{Western University}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{President}{2015 --- 2016}{Health \& Rehabilitation Sciences Graduate Student Society}{Western University}
%	\end{rSubsection}
%	
%	\begin{rSubsection}{Co-organizer}{2016}{Health \& Rehabilitation Sciences Graduate Research Conference}{Western University}
%	\end{rSubsection}
%	
%%	\begin{rSubsection}{Abstract Reviewer}{2015, 2016}{Health \& Rehabilitation Sciences Graduate Research Conference}{Western University}
%%	\end{rSubsection}
%	
%	\begin{rSubsection}{Professional Program Preview Day Volunteer}{2015}{School of Communication Sciences \& Disorders}{Western University}
%	\end{rSubsection}


%----------------------------------------------------------------------------------------
%	 OUTREACH SECTION
%----------------------------------------------------------------------------------------
\bigskip
\begin{center}
	{\bf \emph{Outreach}}\\
%	{\emph{University at Buffalo, Department of Communicative Disorders \& Sciences}
\end{center}
\begin{rSubsection}{Co-founder: R-Ladies}{2017 --- 2019}{London, Ontario Chapter}{London, ON}
	\item Founded and ran a local chapter of R-Ladies Global, ``a world-wide organization to promote gender diversity in the R community."
	\item Curated speakers to give monthly, hands-on workshops on using the R statistical language and programming environment at no cost to members of the London, Ontario community
	\item I would also occasionally lead the workshops (see Teaching: Workshops \& Tutorials)
\end{rSubsection}



\end{rSection}
%----------------------------------------------------------------------------------------
%	PROFESSIONAL DEVELOPMENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Development and Volunteering}

\bigskip
\begin{center}
	{\bf \emph{As faculty member}}\\
\end{center}

	\begin{rSubsection}{Acoustical Society of America School}{Spring 2022}{Acoustical Society of America}{Englewood, CO}
		\item Interdisciplinary early career workshop on acoustics.
	\end{rSubsection}

	\begin{rSubsection}{Evaluating and Facilitating Online Courses: Faculty Academy}{Winter 2022}{University at Buffalo}{Buffalo, NY}
		\item Intensive workshop for faculty to learn to "assess and improve your online course utilizing research-based evaluation tools."
	\end{rSubsection}

	\begin{rSubsection}{Designing and Building Online Courses: Faculty Academy}{Summer 2021}{University at Buffalo}{Buffalo, NY}
		\item Intensive workshop for faculty to learn to "apply and implement best practices for design, assessment, engagement, and technology integration."
	\end{rSubsection}


	\begin{rSubsection}{Pathways Program Attendee}{June 2020}{American Speech-Language-Hearing Association}{Mentorship program (virtual)}
		\item Mentorship program for early career researchers in communication sciences and disorders
		\item "Intended as an initial step to enhance the training, retention, and funding success of clinical scientists in CSD, with the ultimate goal of advancing the evidence base of the discipline."
	\end{rSubsection}

	\begin{rSubsection}{New Faculty Academy Fellow (Scholarly Writing)}{Fall 2019}{University at Buffalo}{Buffalo, NY}
		\item Weekly workshops for new faculty to improve elements of their scholarly research
	\end{rSubsection}

\bigskip

%% REMOVING FOR 2022 VERSION
%\begin{center}
%	{\bf \emph{As graduate student}}\\
%\end{center}
%%------------------------------------------------
%
%	\begin{rSubsection}{Pin Pals Volunteer}{February - March 2016}{Autism Ontario}{London, ON}
%	\item Weekly one-on-one bowling outings with children with autism spectrum disorder
%	
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Operation Smile Volunteer}{September 2015 - June 2016}{Western University}{London, ON}
%	\item Assisted in fundraising for medical charity providing surgical training for doctors treating children born with cleft lip/palate in underfunded international locations
%	
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{IAL Voice Institute Attendee}{June 2015}{International Association of Laryngectomees}{Baltimore, MD}
%	%\item Exposure to comprehensive issues related to laryngectomy and postlaryngectomy patient care
%	%\item Acquired direct, hands-on experience with all methods of alaryngeal speech %including esophageal speech, tracheoesophageal puncture voice restoration, and artificial larynx speech
%	\item Passed IAL examination which confirmed acquisition of basic and intermediate levels of knowledge in postlaryngectomy rehabilitation
%	
%	\end{rSubsection}
%	
%
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Aphasia Retreat Day Volunteer}{May 2015}{Western University}{London, ON}
%	\item Volunteered as "communication ramp" for adults with aphasia during full day retreat
%	\item Facilitated communication using SCAA strategies during games and activities 
%	
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	
%	\begin{rSubsection}{Speech-Language Pathology Assistant}{January 2013 - July 2014}{Speech Therapy Montr\'eal}{Montr\'eal, QC}
%	\item Assisted with early intervention language screenings
%	\item Performed inventory of therapy materials, created client database
%	\end{rSubsection}
%	
%	%------------------------------------------------
%	
%	\begin{rSubsection}{Software Carpentry Bootcamp Attendee}{January 2013}{McGill University}{Montr\'eal, QC}
%	\item Professional development related to programming skill enhancement with command line tools, GitHub, and Python
%	\end{rSubsection}
%	
	%------------------------------------------------
	
%	\begin{rSubsection}{Nor'Easter Marketing Street Team}{August 2008}{Nor'Easter Outdoor Festival}{Burlington, VT}
%	\item Led a Montr\'eal-based team of volunteers responsible for advertising the ``Nor'Easter,'' a large-scale outdoor sports and music festival powered by Eastern Mountain Sports and held in Vermont
%	\end{rSubsection}
	
	%------------------------------------------------
	% REMOVING FOR 2020 VERSION
	
%	\begin{rSubsection}{English Tutor}{September 2007 - July 2008}{ Private family}{Salamanca, Spain}
%	\item Provided daily private English lessons to two Spanish-speaking children
%	\item Created lesson materials including games and conversational practice
%	\end{rSubsection}
	
	%------------------------------------------------

\end{rSection}


%------------------------------
%	HONOURS & AWARDS SECTION
%------------------------------

%\begin{rSection}{Honours \& Awards}
%
%\begin{center}
%	{\bf \emph{Scholarly Awards}}
%\end{center}
%
%%\begin{rSubsection}{Ontario Graduate Scholarship}{2017, 2018}{Province of Ontario Graduate Scholarship Program}{}
%%	\item Value: \$15,000 CAD annually
%%	\item Competitive (merit-based) scholarship
%%\end{rSubsection}
%%
%%\begin{rSubsection}{Western Graduate Research Scholarship}{2014 - 2019}{Western University Graduate Student Funding}{} %Current value: \$19,000 annually}{}
%%	\item Value: approx. \$19,000 CAD annually
%%	\item Western University graduate student stipend
%%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Teaching Award Nominee (not awarded)}{2018}{Western University}{}
%\end{rSubsection}
%
%%\begin{rSubsection}{Graduate Student Research Program Award}{2017-2018}{Parkinson Society Southwestern Ontario}{}
%%	\item Value: \$20,000 CAD
%%\end{rSubsection}
%
%\begin{rSubsection}{Western University ``3 Minute Thesis'' First Place Winner}{2016}{Western University}{}
%	\item  Value: \$1,000 CAD
%\end{rSubsection}
%
%\begin{rSubsection}{Harmonize for Speech Graduate Student Award}{2016}{Harmonize for Speech Ontario}{}
%	\item Value: \$750 CAD
%\end{rSubsection}
%
%\begin{rSubsection}{Student Achievement Award}{2015}{Ontario Association of Speech-Language Pathologists \&
%Audiologists}{}
%	\item Value: OSLA Membership
%\end{rSubsection}
%
%\begin{rSubsection}{Acoustical Society of America Student Poster Honorable Mention}{2015}{Meeting of the 170th Acoustical Society of America}{}
%\end{rSubsection}
%
%\begin{rSubsection}{Best PhD Student Poster Award}{2015}{Health \& Rehabilitation Sciences Graduate Research Conference, Western University}{}
%\end{rSubsection}
%
%%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%
%% TRAVEL
%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{center}
%	{\bf \emph{Travel Awards}}
%\end{center}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Summer)}{2018}{Western University Society of Graduate Students}{}
%	\item Value: \$500.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2018}{Western University Faculty of Health Sciences}{}
%	\item Value: \$250.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Spring)}{2018}{Western University Society of Graduate Students}{}
%	\item Value: \$300.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Subsidy (Spring)}{2016}{Western University Society of Graduate Students}{}
%	\item Value: \$500.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2016}{Western University Health \& Rehabilitation Sciences}{}
%	\item Value: \$400.00
%\end{rSubsection}
%
%\begin{rSubsection}{Graduate Student Conference Travel Award}{2016}{Western University Faculty of Health Sciences}{}
%	\item Value: \$300.00
%\end{rSubsection}
%


%\begin{rSubsection}{Graduation with First Class Honours \& Distinction}{2012}{McGill University}{ }
%\end{rSubsection}
%
%\begin{rSubsection}{Dean's Honour List}{2010}{McGill University}{}
%\end{rSubsection}


\end{rSection}

%\newpage

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & R, Praat, \LaTeX, MatLab, Python \\
%Treatment Programs & LSVT, Melodic Intonation Therapy, Copy \& Recall Treatment \\
\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
%	PROFESSIONAL AFFILIATIONS SECTION
%----------------------------------------------------------------------------------------

%\small{ % make the rest of the sections smaller text. Omit depending on page alignment

\begin{rSection}{Professional Affiliations}
\begin{rSubsection}{Member}{}{}{}
	\item Acoustical Society of America; 2021 --- present
	\item Laboratory Phonology Association; 2020 --- 2022
	\item American Speech-Language-Hearing Association (ASHA); 2019 --- Present
	\item ASHA Special Interest Groups 2, 19; 2016 --- Present
	\item Academy of Neurologic Communication Disorders and Sciences; 2018 --- 2019
	\item Movement Disorders Society; 2016 --- Present
	\item American National Student Speech-Language-Hearing Association; 2016 --- 2019
	\item Ontario Association of Speech-Language Pathologists and Audiologists (Student member); 2014 --- 2019
\end{rSubsection}
%	\begin{rSubsection}{American Speech-Language-Hearing Association}{2019 --- Present}{Member}{}
%	\end{rSubsection}
%	\begin{rSubsection}{ASHA Special Interest Groups 2, 19}{2016 --- Present}{Member}{}
%	\end{rSubsection}
%	\begin{rSubsection}{Academy of Neurologic Communication Disorders and Sciences }{2018 --- 2019}{Member}{}
%	\end{rSubsection}
%	\begin{rSubsection}{Movement Disorders Society}{2016 --- 2019}{Member}{}
%	\end{rSubsection}
%	\begin{rSubsection}{American National Student Speech-Language-Hearing Association}{2016 --- 2019}{Student Member}{}
%	\end{rSubsection}
%	\begin{rSubsection}{Ontario Association of Speech-Language Pathologists and Audiologists}{2014 --- 2019}{Student Member}{}
%	\end{rSubsection}

%\begin{itemize}
%			\renewcommand\labelitemi{$\cdot$}
%	\item American Speech-Language-Hearing Association (ASHA): Member 2019 - present
%	\item Movement Disorders Society (MDS): Member 2016 - present
%	\item Academy of Neurologic Communication Disorders and Sciences (ANCDS): Member 2018 - present
%	\item American National Student Speech-Language-Hearing Association (NSSLHA): Member 2016 - 2019
%	\item Ontario Association of Speech-Language Pathologists and Audiologists (OSLA): Student Member 2014 - 2019
%	\item American Speech-Language-Hearing Association (ASHA) Special Interest Groups 2, 19
%\end{itemize}

\end{rSection}

%%\newpage
%----------------------------------------------------------------------------------------
%	EXTRACURRICULARS  SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Personal Interests}
%
%\begin{itemize}
%%			\renewcommand\labelitemi{$\cdot$} 
%	\item Rock climbing: competed in three US National Championships and one North American Continental Championship
%	\item Long-distance running: completed two marathons and two half marathons
%	\item Coffee preparation science: former Director of Quality Control at Caf\'e Myriade, current hobbyist
%\end{itemize}
%
%\end{rSection}

%----------------------------------------------------------------------------------------
%	OTHER INFO  SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Other information}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Citizenship & United States, Canada\\
Languages & English (native), Spanish (advanced), French (novice) \\
\end{tabular}

\end{rSection}

%} %end small

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------
\end{document}
